Summary {.storyboard data-navmenu="2020"}
=========================================


###  Attendees {data-commentary-width=400}

```{r cy2020_setup,eval=F}
Attendance2020 %>% summary_setup %>%
  plot_ly(x = ~reorder(Semester,ID), y = ~Total, type = "bar", 
          name = "Total Number of Attendees per Semester") %>%
  layout(xaxis = list(title = 'Semester'), yaxis = list(title = '' ))
```


```{r cy2020_attendee_summary,echo=F}
Attendance2020 %>% attendeetotal ->  Attendees_Total
Attendance2020 %>% attendeeunique -> Attendees_Unique
full_join(Attendees_Total,Attendees_Unique) -> Attendance2020_Summary
plot_ly(data=Attendance2020_Summary, 
        x = ~reorder(Semester,ID), y = ~Attendees, 
        type = "bar", 
        name = "Total Attendees") %>%
    add_trace(y =  ~ Unique, name = "Unique Attendees") %>%
  layout(xaxis = list(title = 'Semester'), yaxis = list(title = '' ))
```

*** 

```{r cy2020_attendee_total,echo=F}
Attendance2020 %>% attendeetotal ->  Attendees_Total
Attendance2020 %>% attendeeunique -> Attendees_Unique
full_join(Attendees_Total,Attendees_Unique) %>% select(-ID) -> tmp
tmp1 <- tribble(
  ~Semester,~Sessions,~Attendees,~Unique,
  "",sum(tmp$Sessions),sum(tmp$Attendees),sum(tmp$Unique)) 
bind_rows(tmp,tmp1) %>% kable()

Attendance2020 %>% attendeedesc %>% kable()
```

### Attendees Status

```{r cy2020_attendee_status,echo=F}
Attendance2020 %>% attendeestatus %>%
  plot_ly(x = ~reorder(Semester,ID), y = ~Total, color = ~Status, type = "bar")%>%
  layout(xaxis = list(title = 'Semester'), yaxis = list(title = '' ))
```

***

```{r cy2020_total_attendee_status,echo=F}
Attendance2020 %>% attendeestatustotal -> total_attendee
Attendance2020 %>% attendeestatusunique -> unique_attendee
full_join(total_attendee,unique_attendee) -> tmp
add_row(tmp,Status="",Attendees=sum(tmp$Attendees),Unique=sum(tmp$Unique)) %>% kable()
```


### Attendees per Session

```{r cy2020_attendee_session,echo=F}
Attendance2020 %>% attendeesession %>%
  plot_ly(x = ~reorder(Semester,ID), y = ~Total, color = ~Session, type = "bar")%>%
  layout(xaxis = list(title = 'Semester'), yaxis = list(title = '' ), barmode = 'stack')
```

### Departments/Majors represented by Attendees {data-commentary-width=600}


```{r cy2020_attendee_dept,echo=F}
Attendance2020 %>% attendeedept -> tmp1
Attendance2020 %>% attendeedeptunique -> tmp2
full_join(tmp2,tmp1) %>% datatable()
```

*** 

```{r cy2020_attendee,echo=F}
Attendance2020 %>% deptunique -> Department_Unique
Attendance2020 %>% depttotal -> Department_Total
full_join(Attendees_Total,Department_Unique) %>% select(-ID) -> tmp
tmp1 <- tribble(
   ~Semester,~Sessions,~Attendees,~Department,
   "",sum(tmp$Sessions),sum(tmp$Attendees),sum(tmp$Department))
bind_rows(tmp,tmp1) %>% kable()
```

```{r cy2020_college,echo=F}
Attendance2020 %>% collegetotal -> total_attendee
Attendance2020 %>% collegeunique -> unique_attendee
full_join(total_attendee,unique_attendee) -> tmp 
add_row(tmp,College="",Attendees=sum(tmp$Attendees),Unique=sum(tmp$Unique)) %>% kable()
```



Spring 2020 {.storyboard data-navmenu="2020"}
=========================================

### Summary {data-commentary-width=400}

```{r spring2020_setup,echo=F,warning=F,include=F}
Spring2020 %>% sem_status -> Spring2020Status
Spring2020 %>% sem_unique -> Spring2020StatusUnique
full_join(Spring2020Status,Spring2020StatusUnique,by="Status") %>%
  summarise_if(is.numeric,sum) -> Spring2020Total
```


```{r spring2020_attendee,echo=F}
Spring2020 %>% sem_attendee("Session","Status") %>%
  plot_ly(x = ~ Session, y= ~ Attendees, color = ~ Status, type = "bar")
```


*** 

```{r spring2020_attendee_summary,echo=F}
full_join(Spring2020Status,Spring2020StatusUnique,by="Status")  %>%
  add_row(Status=" ",
          Total=Spring2020Total$Total, 
          Unique=Spring2020Total$Unique) %>% kable()
Spring2020 %>% sem_attendee_session %>% kable()
```

### Attendees by Session

```{r spring2020_attendee_session}
Spring2020 %>% sem_attendee("Session","Status") %>%
  spread(Status,Attendees,fill=0) %>% kable()
Spring2020 %>% sem_attendee("Session","Department") %>%
  spread(Session,Attendees,fill=0) %>% 
  datatable(filter = 'top', 
            options = list(pageLength = 50, autoWidth = TRUE)
            )
```

### Department/Majors represented by Attendees

```{r spring2020_attendee_dept,echo=F}
Spring2020 %>% sem_attendee_dept %>%
  plot_ly(x = ~ Total, y = ~ reorder(Department,Total), type = "bar") %>%
  layout(yaxis = list(title = ' Department/Major' ), 
     xaxis = list(title = '' ),
     margin = list(l = 250, r = 20, t = 25, b = 25))
```

***

```{r spring2020_college,echo=F}
Spring2020 %>% collegetotal -> total_attendee
Spring2020 %>% collegeunique -> unique_attendee
full_join(total_attendee,unique_attendee) -> tmp 
add_row(tmp,College="",Attendees=sum(tmp$Attendees),Unique=sum(tmp$Unique)) %>% kable()
```




Fall 2020 {.storyboard data-navmenu="2020"}
=========================================

### Summary {data-commentary-width=400}

```{r fall2020_setup,echo=F,warning=F,include=F}
Fall2020 %>% sem_status -> Fall2020Status
Fall2020 %>% sem_unique -> Fall2020StatusUnique
full_join(Fall2020Status,Fall2020StatusUnique,by="Status") %>%
  summarise_if(is.numeric,sum) -> Fall2020Total
```


```{r fall2020_attendee,echo=F}
Fall2020 %>% sem_attendee("Session","Status") %>%
  plot_ly(x = ~ Session, y= ~ Attendees, color = ~ Status, type = "bar")
```


*** 

```{r fall2020_attendee_summary,echo=F}
full_join(Fall2020Status,Fall2020StatusUnique,by="Status")  %>%
  add_row(Status=" ",
          Total=Fall2020Total$Total, 
          Unique=Fall2020Total$Unique) %>% kable()
Fall2020 %>% sem_attendee_session %>% kable()
```

### Attendees by Session

```{r fall2020_attendee_session}
Fall2020 %>% sem_attendee("Session","Status") %>%
  spread(Status,Attendees,fill=0) %>% kable()
Fall2020 %>% sem_attendee("Session","Department") %>%
  spread(Session,Attendees,fill=0) %>% 
  datatable(filter = 'top', 
            options = list(pageLength = 50, autoWidth = TRUE)
            )
```

### Department/Majors represented by Attendees

```{r fall2020_attendee_dept,echo=F}
Fall2020 %>% sem_attendee_dept %>%
  plot_ly(x = ~ Total, y = ~ reorder(Department,Total), type = "bar") %>%
  layout(yaxis = list(title = ' Department/Major' ), 
     xaxis = list(title = '' ),
     margin = list(l = 250, r = 20, t = 25, b = 25))
```

***

```{r fall2020_college,echo=F}
Fall2020 %>% collegetotal -> total_attendee
Fall2020 %>% collegeunique -> unique_attendee
full_join(total_attendee,unique_attendee) -> tmp 
add_row(tmp,College="",Attendees=sum(tmp$Attendees),Unique=sum(tmp$Unique)) %>% kable()
```



