---
title: "AY 19-20 Report"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    source: embed
    smart: false
    theme: lumen
    navbar: 
      - { title: "Usage Summary", href: "https://webapps.lehigh.edu/hpc/usage/dashboard.html"}
      - { title: "Daily Monitoring", href: "https://webapps.lehigh.edu/hpc/monitor"}
      - { title: "AY 18-19 Report", href: "https://webapps.lehigh.edu/hpc/monitor/ay1819.html"} 
      - { title: "AY 17-18 Report", href: "https://webapps.lehigh.edu/hpc/monitor/ay1718.html"} 
      - { title: "AY 16-17 Report", href: "https://webapps.lehigh.edu/hpc/monitor/ay1617.html"} 
---

```{r setup, include=F}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(reshape2)
library(stringr)
library(plotly)
library(knitr)
library(DT)
options(DT.options = list(dom = 'ltip', pageLength = 25, lengthMenu = c(10, 25, 50, 75, 100), autoWidth = TRUE) )
library(kableExtra)
options(knitr.table.format = "html")
source("./ayfuncs.R")

```

Summary {data-navmenu="Annual Report"}
==============================

```{r annual-setup,echo=F}
jobsthisay <- read_delim('jobsalloc1920.csv.gz',delim=";")

dayspermonth = c(31,30,31,31,29,31,30,31,30,31,31,30)
lts <- rep(20,12)*9*dayspermonth*24
im1080 <- rep(25,12)*24*dayspermonth*24
eng <- rep(8,12)*24*dayspermonth*24
engc <- rep(14,12)*24*dayspermonth*24
himem <- rep(1,12)*16*dayspermonth*24
enge <- c(10,10,10,10,10,10,10,10,8,8,8,8)*36*c(31,30,31,31,29,31,30,31,30,31,31,30)*24
engi <- rep(2,12)*36*dayspermonth*24
im2080 <- rep(12,12)*36*dayspermonth*24
chem <- rep(6,12)*36*c(0,0,0,0,0,0,0,2,30,31,31,30)*24
health <- rep(2,12)*36*c(0,0,0,0,0,0,0,0,0,0,31,30)*24
ay1920su <- lts+im1080+eng+engc+himem+enge+engi+im2080+chem+health
if ( day_of_month > 1 ){
  currmonth <- length(seq(from=as.Date("2019-10-01"), to=as.Date("2020-09-30"), by='month'))
} else {
  currmonth <- length(seq(from=as.Date("2019-10-01"), to=as.Date("2020-09-30"), by='month'))
}
# read power and energy usage
read_csv('../dashboard/monthlypower1920.csv') %>% 
  mutate(Year=year(Month),Month=month(Month,label=TRUE)) %>%
  select(c(Year,Month,Partition,Host,Power,Energy)) -> monthlypower1920
read_csv('../dashboard/dailypower1920.csv') %>%
  mutate(Year=year(Date),Month=month(Date,label=TRUE),Day=day(Date)) %>%
  select(c(Date,Year,Month,Day,Partition,Host,Power,Energy)) -> dailypower1920

jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>% 
  group_by(Year,Month) %>% 
  select(c(Month,Start,Submit,End,NCPUS))  %>% 
  summarize( 
    Total_SU=round(sum(as.numeric(difftime(End,Start,units="hours"))*NCPUS),2), 
    Total_Jobs=n() 
  ) -> percent
```

Row
-------------------------------------


```{r annualsummary}
jobsthisay %>% summary %>% 
   mutate(Partition="Total",Used=round(SU/sum(ay1920su[1:currmonth])*100,2)) %>%
   select(c(Partition,SU,'% Consumed'=Used,Jobs,Wait,Run)) -> Total_SU_Jobs
jobsthisay %>% serial_filter %>% summary %>% 
  mutate(Partition="Total",
         SUper = round(SU/Total_SU_Jobs$SU*100,2), 
         Jobsper = round(Jobs/Total_SU_Jobs$Jobs*100,2)) %>%
  select(c(Partition,SU,Jobs,'% SU'=SUper,'% Jobs'=Jobsper,Wait,Run)) -> serialtotal
jobsthisay %>% smp_filter %>% summary %>% 
  mutate(Partition="Total",
         SUper = round(SU/Total_SU_Jobs$SU*100,2), 
         Jobsper = round(Jobs/Total_SU_Jobs$Jobs*100,2)) %>%
  select(c(Partition,SU,Jobs,'% SU'=SUper,'% Jobs'=Jobsper,Wait,Run)) -> smptotal
jobsthisay %>% dmp_filter %>% summary %>% 
  mutate(Partition="Total",
         SUper = round(SU/Total_SU_Jobs$SU*100,2), 
         Jobsper = round(Jobs/Total_SU_Jobs$Jobs*100,2)) %>%
  select(c(Partition,SU,Jobs,'% SU'=SUper,'% Jobs'=Jobsper,Wait,Run)) -> dmptotal
```

### Total

```{r annualsummary-total}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% summary %>% partfilter('lts',lts) -> ltstotal
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% summary %>% partfilter('im1080',im1080) -> im1080total
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% summary %>% partfilter('im2080',im2080) -> im2080total
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% summary %>% partfilter('eng',eng) -> engtotal
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% summary %>% partfilter('engc',engc) -> engctotal
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% summary %>% partfilter('himem',himem) -> himemtotal
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% summary %>% partfilter('enge',enge) -> engetotal
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% summary %>% partfilter('engi',engi) -> engitotal
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% summary %>% partfilter('chem',chem) -> chemtotal
jobsthisay %>% filter(str_detect(Partition,'health')) %>% summary %>% partfilter('health',health) -> healthtotal
rbind(Total_SU_Jobs,ltstotal,im1080total,engtotal,engctotal,himemtotal,engetotal,engitotal,im2080total,chemtotal,healthtotal) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r annualsummary-serial}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% 
  serial_filter %>% summary %>% parttotalfilter('lts',ltstotal) -> lts_serial
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% 
  serial_filter %>% summary %>% parttotalfilter('im1080',im1080total) -> im1080_serial
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% 
  serial_filter %>% summary %>% parttotalfilter('im2080',im2080total) -> im2080_serial
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% 
  serial_filter %>% summary %>% parttotalfilter('eng',engtotal) -> eng_serial
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% 
  serial_filter %>% summary %>% parttotalfilter('engc',engctotal) -> engc_serial
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% 
  serial_filter %>% summary %>% parttotalfilter('himem',himemtotal) -> himem_serial
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% 
  serial_filter %>% summary %>% parttotalfilter('enge',engetotal) -> enge_serial
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% 
  serial_filter %>% summary %>% parttotalfilter('engi',engitotal) -> engi_serial
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% 
  serial_filter %>% summary %>% parttotalfilter('chem',chemtotal) -> chem_serial
jobsthisay %>% filter(str_detect(Partition,'health')) %>% 
  serial_filter %>% summary %>% parttotalfilter('health',healthtotal) -> health_serial
rbind(serialtotal,lts_serial,im1080_serial,eng_serial,engc_serial,himem_serial,enge_serial,engi_serial,im2080_serial,chem_serial,health_serial) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r annualsummary-smp}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% 
  smp_filter %>% summary %>% parttotalfilter('lts',ltstotal) -> lts_smp
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% 
  smp_filter %>% summary %>% parttotalfilter('im1080',im1080total) -> im1080_smp
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% 
  smp_filter %>% summary %>% parttotalfilter('im2080',im2080total) -> im2080_smp
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% 
  smp_filter %>% summary %>% parttotalfilter('eng',engtotal) -> eng_smp
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% 
  smp_filter %>% summary %>% parttotalfilter('engc',engctotal) -> engc_smp
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% 
  smp_filter %>% summary %>% parttotalfilter('himem',himemtotal) -> himem_smp
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% 
  smp_filter %>% summary %>% parttotalfilter('enge',engetotal) -> enge_smp
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% 
  smp_filter %>% summary %>% parttotalfilter('engi',engitotal) -> engi_smp
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% 
  smp_filter %>% summary %>% parttotalfilter('chem',chemtotal) -> chem_smp
jobsthisay %>% filter(str_detect(Partition,'health')) %>% 
  smp_filter %>% summary %>% parttotalfilter('health',healthtotal) -> health_smp
rbind(smptotal,lts_smp,im1080_smp,eng_smp,engc_smp,himem_smp,enge_smp,engi_smp,im2080_smp,chem_smp,health_smp) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r annualsummary-dmp}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('lts',ltstotal) -> lts_dmp
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('im1080',im1080total) -> im1080_dmp
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('im2080',im2080total) -> im2080_dmp
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% 
  dmp_filter %>% summary %>% parttotalfilter('eng',engtotal) -> eng_dmp
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('engc',engctotal) -> engc_dmp
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('himem',himemtotal) -> himem_dmp
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('enge',engetotal) -> enge_dmp
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('engi',engitotal) -> engi_dmp
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('chem',chemtotal) -> chem_dmp
jobsthisay %>% filter(str_detect(Partition,'health')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('health',healthtotal) -> health_dmp
rbind(smptotal,lts_smp,im1080_smp,eng_smp,engc_smp,himem_smp,enge_smp,engi_smp,im2080_smp,chem_smp,health_dmp) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```


Row
--------------------------------------------------

### CPU vs GPU

```{r annualcpuvgpu-summary,echo=F}
jobsthisay %>% summary -> Timing_Total
jobsthisay %>% filter(!str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="cpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> cpu
jobsthisay %>% filter(str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="gpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> gpu
jobsthisay %>% summary %>% 
   mutate(Type="Total","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> total
full_join(full_join(cpu,gpu),total) %>% my_table
```

### Serial Jobs

```{r annualcpuvgpu-serial,echo=F}
jobsthisay %>% serial_filter %>% filter(!str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="cpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> cpu
jobsthisay %>% serial_filter %>% filter(str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="gpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> gpu
jobsthisay %>% serial_filter %>% summary %>% 
   mutate(Type="Total","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> total
full_join(full_join(cpu,gpu),total) %>% my_table
```

### SMP Jobs

```{r annualcpuvgpu-smp,echo=F}
jobsthisay %>% smp_filter %>% filter(!str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="cpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> cpu
jobsthisay %>% smp_filter %>% filter(str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="gpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> gpu
jobsthisay %>% smp_filter %>% summary %>% 
   mutate(Type="Total","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> total
full_join(full_join(cpu,gpu),total) %>% my_table
```

### DMP Jobs

```{r annualcpuvgpu-dmp,echo=F}
jobsthisay %>% dmp_filter %>% filter(!str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="cpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> cpu
jobsthisay %>% dmp_filter %>% filter(str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="gpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> gpu
jobsthisay %>% dmp_filter %>% summary %>% 
   mutate(Type="Total","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> total
full_join(full_join(cpu,gpu),total) %>% my_table
```

Partition {data-navmenu="Annual Report"}
==============================


Row
---------------------------------

### Summary

```{r annualpart-summary,echo=F}
jobsthisay %>% group_by(Partition) %>% summary -> Timing_Part
jobsthisay %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) %>% mutate('% SU' = round(SU/Timing_Total$SU*100,2)) %>% select(c('Partition','SU','% SU','Jobs', 'Wait', 'Run')) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```


### Serial Jobs

```{r annualpart-serial,echo=F}
jobsthisay %>% serial_filter %>% group_by(Partition) %>% summary  -> Timing_Part
jobsthisay %>% serial_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### SMP Jobs

```{r annualpart-smp,echo=F}
jobsthisay %>% smp_filter %>% group_by(Partition) %>% summary  -> Timing_Part
jobsthisay %>% smp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### DMP Jobs

```{r annualpart-dmp,echo=F}
jobsthisay %>% dmp_filter %>% group_by(Partition) %>% summary  -> Timing_Part
jobsthisay %>% dmp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```





Allocation {data-navmenu="Annual Report"}
==============================

Row
---------------------------------

### Summary

```{r annualalloc-summary,echo=F}
jobsthisay %>% group_by(Account) %>% summary  -> Timing_Part
jobsthisay %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### CPU vs GPU

```{r annualalloc-type,echo=F}
jobsthisay %>% cpu_gpu_total(Account) -> total
jobsthisay %>% cpu_total(Account) -> cpu
jobsthisay %>% gpu_total(Account) -> gpu
full_join(total,full_join(cpu,gpu)) -> usage1920
usage1920[is.na(usage1920)] <- 0
usage1920 %>% mutate('%CPU'=round(CPU/Total*100,2), '%GPU'=round(GPU/Total*100,2)) %>% my_table
```


### Serial Jobs

```{r annualalloc-serial,echo=F}
jobsthisay %>% serial_filter %>% group_by(Account) %>% summary  -> Timing_Part
jobsthisay %>% serial_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table 
```

### SMP Jobs

```{r annualalloc-smp,echo=F}
jobsthisay %>% smp_filter %>% group_by(Account) %>% summary  -> Timing_Part
jobsthisay %>% smp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### DMP Jobs

```{r annualalloc-dmp,echo=F}
jobsthisay %>% dmp_filter %>% group_by(Account) %>% summary  -> Timing_Part
jobsthisay %>% dmp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table 
```

User {data-navmenu="Annual Report"}
==============================

Row
---------------------------------

### Summary

```{r annualuser-summary}
jobsthisay %>% group_by(User) %>% summary  -> Timing_Part
jobsthisay %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### CPU vs GPU

```{r annualuser-type,echo=F}
jobsthisay %>% cpu_gpu_total(User) -> total
jobsthisay %>% cpu_total(User) -> cpu
jobsthisay %>% gpu_total(User) -> gpu
full_join(total,full_join(cpu,gpu)) -> usage1920
usage1920[is.na(usage1920)] <- 0
usage1920 %>% mutate('%CPU'=round(CPU/Total*100,2), '%GPU'=round(GPU/Total*100,2)) %>% my_table
```

### Serial

```{r annualuser-serial}
jobsthisay %>% serial_filter %>% group_by(User) %>% summary  -> Timing_Part
jobsthisay %>% serial_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table 
```

### SMP

```{r annualuser-smp}
jobsthisay %>% smp_filter %>% group_by(User) %>% summary  -> Timing_Part
jobsthisay %>% smp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### DMP

```{r annualuser-dmp}
jobsthisay %>% dmp_filter %>% group_by(User) %>% summary  -> Timing_Part
jobsthisay %>% dmp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```


Summary {data-navmenu="Monthly Reports"}
=========================================

Row 
------------------------------------

### Summary

```{r monthly-setup,echo=F}
jobsthisay %>% monthly_summary %>% partpercent(ay1920su) -> total
jobsthisay %>% serial_filter %>% monthly_summary -> serial
jobsthisay %>% smp_filter %>% monthly_summary -> smp
jobsthisay %>% dmp_filter %>% monthly_summary -> dmp

getpercent(serial,percent) -> serialpercent
getpercent(smp,percent) -> smppercent
getpercent(dmp,percent) -> dmppercent

#cbind(total,serialpercent,smppercent,dmppercent)  %>% select(-c(Year1,Month1,Year2,Month2,Year3,Month3)) -> jobtotal
#colnames(jobtotal) <- c("Year","Month","SU","Jobs","Wait","Run","SU","Jobs","% SU","%Jobs","Wait","Run","SU","Jobs","% SU","%Jobs","Wait","Run","SU","Jobs","% SU","%Jobs","Wait","Run")
#jobtotal %>% 
#  kable() %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive")) %>%
#  add_header_above(c(" " = 2, "Total" = 4, "Serial" = 6, "SMP" = 6, "DMP" = 6))
```


```{r monthly-summary}
total %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### CPU vs GPU

```{r monthly-summarytype, echo=F}
jobsthisay %>% cpu_gpu_monthly -> total
jobsthisay %>% cpu_monthly -> cpu
jobsthisay %>% gpu_monthly -> gpu
full_join(total,full_join(cpu,gpu)) %>% mutate('%CPU'=round(CPU/Total*100,2), '%GPU'=round(GPU/Total*100,2)) -> usage1920
usage1920 %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthly-serial}
serialpercent %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthly-smp}
smppercent %>% 
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthly-dmp}
dmppercent %>% 
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Partition {data-navmenu="Monthly Reports"}
===============================================

Row 
------------------------------------------

### lts

```{r monthlypart-lts}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% monthly_summary %>% partpercent(lts[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-lts-serial}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% serial_filter %>% monthly_summary %>% 
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthly-part-lts-smp}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-lts-dmp}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### im1080

```{r monthlypart-im1080}
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% monthly_summary %>% partpercent(im1080[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-im1080-serial}
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-im1080-smp}
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-im1080-dmp}
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### eng

```{r monthlypart-eng}
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% monthly_summary %>% partpercent(eng[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-eng-serial}
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-eng-smp}
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-eng-dmp}
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### engc

```{r monthlypart-engc}
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% monthly_summary %>% partpercent(engc[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-engc-serial}
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-engc-smp}
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-engc-dmp}
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### himem

```{r monthlypart-himem}
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% monthly_summary %>% partpercent(himem[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-himem-serial}
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-himem-smp}
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-himem-dmp}
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### enge

```{r monthlypart-enge}
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% monthly_summary %>% partpercent(enge[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-enge-serial}
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-enge-smp}
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-enge-dmp}
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### engi

```{r monthlypart-engi}
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% monthly_summary %>% partpercent(engi[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-engi-serial}
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-engi-smp}
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-engi-dmp}
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```



Row 
------------------------------------------

### im2080

```{r monthlypart-im2080}
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% monthly_summary %>% partpercent(im2080[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-im2080-serial}
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-im2080-smp}
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-im2080-dmp}
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### chem

```{r monthlypart-chem}
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% monthly_summary %>% partpercent(chem[8:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-chem-serial}
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-chem-smp}
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-chem-dmp}
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### health

```{r monthlypart-health}
jobsthisay %>% filter(str_detect(Partition,'health')) %>% monthly_summary %>% partpercent(health[10:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-health-serial}
jobsthisay %>% filter(str_detect(Partition,'health')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-health-smp}
jobsthisay %>% filter(str_detect(Partition,'health')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-health-dmp}
jobsthisay %>% filter(str_detect(Partition,'health')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```






Allocation {data-navmenu="Monthly Reports"}
==========================================

Row
---------------------------------

### List of PIs

```{r monthlyalloc-list,echo=F}
jobsthisay$Account %>% unique %>% sort %>% matrix(ncol = 1) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped", full_width = F)
```

### Summary

```{r monthlyalloc-summary,echo=F}
jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>%
  group_by(Year,Month,Account) %>%
  summary %>%
  my_longtable
```

### Partition

```{r monthlyalloc-part,echo=F}
jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>%
  group_by(Year,Month,Account,Partition) %>%
  summary %>%
  my_longtable
```

User {data-navmenu="Monthly Reports"}
==========================================

Row
---------------------------------

### List of Users

```{r monthlyuser-list,echo=F}
jobsthisay$User %>% unique %>% sort %>% matrix(ncol = 1) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped")
```

### Summary

```{r monthlyuser-summary,echo=F}
jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>%
  group_by(Year,Month,User,Account) %>%
  summary %>%
  my_longtable
```

### Partition

```{r monthlyuser-part,echo=F}
jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>%
  group_by(Year,Month,User,Account,Partition) %>%
  summary %>%
  my_longtable
```

Energy Consumption {data-navmenu="Monthly Reports"} 
=====================================================

Row
-------------------------------------------

### Total 

```{r monthlyenergy-total}
monthlypower1920 %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### lts

```{r monthlyenergy-lts}
monthlypower1920 %>% filter(str_detect(Partition,'lts')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage(kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```


### im1080

```{r monthlyenergy-im1080}
monthlypower1920 %>% filter(str_detect(Partition,'im1080')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```


### eng

```{r monthyenergy-eng}
monthlypower1920 %>% filter(Partition=="eng" | Partition=="eng-gpu") %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### engc

```{r monthlyenergy-engc}
monthlypower1920 %>% filter(str_detect(Partition,'engc')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

Row
---------------------------------------------


```{r monthlyenergy-himem}
### himem
# himem node can only measure volts, no amp or watts skipping this node
#monthlypower1920 %>% filter(str_detect(Partition,'himem')) %>%
#  group_by(Year,Month) %>%
#  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
#  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### enge

```{r monthlyenergy-enge}
monthlypower1920 %>% filter(str_detect(Partition,'enge')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### engi

```{r monthlyenergy-engi}
monthlypower1920 %>% filter(str_detect(Partition,'engi')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### im2080

```{r monthlyenergy-im2080}
monthlypower1920 %>% filter(str_detect(Partition,'im2080')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### chem

```{r monthlyenergy-chem}
monthlypower1920 %>% filter(str_detect(Partition,'chem')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```


Row
---------------------------------------------

### Energy Consumption per Server

```{r monthylenergy-server}
monthlypower1920 %>%
  group_by(Year,Month,Partition,Host) %>%
  summarize('Average Power Usage (W)'=round(sum(Power),2),'Energy Consumption (kWh)'=round(sum(Energy),2)) %>%
  my_longtable  
```



Jobs Completed 
==========================================

Row {.tabset data-height=1500}
----------------------------------

### October

```{r october,echo=F}
monthly_usage( jobsthisay, as.Date("2019-10-01"), as.Date("2019-11-01") )
```

### November

```{r november,echo=F}
monthly_usage( jobsthisay, as.Date("2019-11-01"), as.Date("2019-12-01") )
```

### December

```{r december,echo=F}
monthly_usage( jobsthisay, as.Date("2019-12-01"), as.Date("2020-01-01") )
```

### January

```{r january,echo=F}
monthly_usage( jobsthisay, as.Date("2020-01-01"), as.Date("2020-02-01") )
```

### February

```{r february,echo=F}
monthly_usage( jobsthisay, as.Date("2020-02-01"), as.Date("2020-03-01") )
```

### March

```{r march,echo=F}
monthly_usage( jobsthisay, as.Date("2020-03-01"), as.Date("2020-04-01") )
```

### April

```{r april,echo=F}
monthly_usage( jobsthisay, as.Date("2020-04-01"), as.Date("2020-05-01") )
```

### May

```{r may,echo=F}
monthly_usage( jobsthisay, as.Date("2020-05-01"), as.Date("2020-06-01") )
```

### June

```{r june,echo=F}
monthly_usage( jobsthisay, as.Date("2020-06-01"), as.Date("2020-07-01") )
```

### July

```{r july,echo=F}
monthly_usage( jobsthisay, as.Date("2020-07-01"), as.Date("2020-08-01") )
```

### August

```{r august,echo=F}
monthly_usage( jobsthisay, as.Date("2020-08-01"), as.Date("2020-09-01") )
```

### September

```{r september,echo=F}
monthly_usage( jobsthisay, as.Date("2020-09-01"), as.Date("2020-10-01") )
```

