---
title: "CY 2021 Report"
output:
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: scroll
    source: embed
    smart: false
    theme: lumen
    navbar: 
      - { title: "Usage Summary", href: "https://webapps.lehigh.edu/hpc/usage/dashboard.html"}
      - { title: "Daily Monitoring", href: "https://webapps.lehigh.edu/hpc/monitor"}
---

```{r setup, include=F}
library(flexdashboard)
library(tidyverse)
library(lubridate)
library(reshape2)
library(stringr)
library(plotly)
library(knitr)
library(DT)
options(DT.options = list(dom = 'ltip', pageLength = 25, lengthMenu = c(10, 25, 50, 75, 100), autoWidth = TRUE) )
library(kableExtra)
options(knitr.table.format = "html")
source("./ayfuncs.R")

```

Summary {data-navmenu="Annual Report"}
==============================

```{r annual-setup,echo=F}
jobsthisay2021 <- read_delim('jobsalloc2021.csv.gz',delim=";") 
jobsthisay2122 <- read_delim('jobsalloc.csv.gz',delim=";") 
jobsthisay <- rbind(jobsthisay2021,jobsthisay2122) %>%
	filter(End >= as.Date("2021-01-01") & End < as.Date("2022-01-01")) %>%
	separate(Account, c("Account", "year1", "year2") , sep="_", fill = "right") %>% select(-c("year1","year2"))

dayspermonth = c(31,28,31,30,31,30,31,31,30,31,30,31)
lts <- rep(20,12)*9*dayspermonth*24
im1080 <- rep(25,12)*24*dayspermonth*24
eng <- rep(8,12)*24*dayspermonth*24
engc <- rep(14,12)*24*dayspermonth*24
himem <- rep(1,12)*16*dayspermonth*24
enge <- rep(8,12)*36*dayspermonth*24
engi <- rep(2,12)*36*dayspermonth*24
im2080 <- rep(12,12)*36*dayspermonth*24
chem <- rep(6,12)*36*dayspermonth*24
health <- rep(2,12)*36*dayspermonth*24
hawkcpu <- rep(26,12)*52*dayspermonth*24
hawkgpu <- rep(4,12)*48*dayspermonth*24
hawkmem <- rep(4,12)*52*dayspermonth*24
infolab <- rep(2,12)*52*dayspermonth*24
ay2021su <- lts+im1080+eng+engc+himem+enge+engi+im2080+chem+health+hawkcpu+hawkgpu+hawkmem+infolab
if ( Sys.Date() > as.Date("2021-12-31")){
  currmonth <- length(seq(from=as.Date("2021-01-01"), to=as.Date("2021-12-31"), by='month'))
} else {
  if ( day_of_month > 1 ){
    currmonth <- length(seq(from=as.Date("2021-01-01"), to=Sys.Date(), by='month'))
  } else {
    currmonth <- length(seq(from=as.Date("2021-01-01"), to=Sys.Date()-1, by='month'))
  }
}
# read power and energy usage
read_csv('../dashboard/monthlypower.csv') %>% 
  filter(Month >= as.Date("2021-01-01") & Month < as.Date("2022-01-01")) %>%
  mutate(Year=year(Month),Month=month(Month,label=TRUE)) %>%
  select(c(Year,Month,Partition,Host,Power,Energy)) -> monthlypower2021
read_csv('../dashboard/dailypower.csv') %>% 
  filter(Date >= as.Date("2021-01-01") & Date < as.Date("2022-01-01")) %>%
  mutate(Year=year(Date),Month=month(Date,label=TRUE),Day=day(Date)) %>%
  select(c(Date,Year,Month,Day,Partition,Host,Power,Energy)) -> dailypower2021

jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>% 
  group_by(Year,Month) %>% 
  select(c(Month,Start,Submit,End,NCPUS))  %>% 
  summarize( 
    Total_SU=round(sum(as.numeric(difftime(End,Start,units="hours"))*NCPUS),2), 
    Total_Jobs=n() 
  ) -> percent
```

Row
-------------------------------------



```{r annualsummary}
jobsthisay %>% summary %>% 
   mutate(Partition="Total",Used=round(SU/sum(ay2021su[1:currmonth])*100,2)) %>%
   select(c(Partition,SU,'% Consumed'=Used,Jobs,Wait,Run)) -> Total_SU_Jobs
jobsthisay %>% serial_filter %>% summary %>% 
  mutate(Partition="Total",
         SUper = round(SU/Total_SU_Jobs$SU*100,2), 
         Jobsper = round(Jobs/Total_SU_Jobs$Jobs*100,2)) %>%
  select(c(Partition,SU,Jobs,'% SU'=SUper,'% Jobs'=Jobsper,Wait,Run)) -> serialtotal
jobsthisay %>% smp_filter %>% summary %>% 
  mutate(Partition="Total",
         SUper = round(SU/Total_SU_Jobs$SU*100,2), 
         Jobsper = round(Jobs/Total_SU_Jobs$Jobs*100,2)) %>%
  select(c(Partition,SU,Jobs,'% SU'=SUper,'% Jobs'=Jobsper,Wait,Run)) -> smptotal
jobsthisay %>% dmp_filter %>% summary %>% 
  mutate(Partition="Total",
         SUper = round(SU/Total_SU_Jobs$SU*100,2), 
         Jobsper = round(Jobs/Total_SU_Jobs$Jobs*100,2)) %>%
  select(c(Partition,SU,Jobs,'% SU'=SUper,'% Jobs'=Jobsper,Wait,Run)) -> dmptotal
```

### Total

```{r annualsummary-total}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% summary %>% partfilter('lts',lts) -> ltstotal
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% summary %>% partfilter('im1080',im1080) -> im1080total
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% summary %>% partfilter('im2080',im2080) -> im2080total
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% summary %>% partfilter('eng',eng) -> engtotal
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% summary %>% partfilter('engc',engc) -> engctotal
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% summary %>% partfilter('himem',himem) -> himemtotal
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% summary %>% partfilter('enge',enge) -> engetotal
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% summary %>% partfilter('engi',engi) -> engitotal
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% summary %>% partfilter('chem',chem) -> chemtotal
jobsthisay %>% filter(str_detect(Partition,'health')) %>% summary %>% partfilter('health',health) -> healthtotal
jobsthisay %>% filter(str_detect(Partition,'hawkcpu') | str_detect(Partition,'hawktest')) %>% summary %>% partfilter('hawkcpu',hawkcpu) -> hawkcputotal
jobsthisay %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>% summary %>% partfilter('hawkgpu',hawkgpu) -> hawkgputotal
jobsthisay %>% filter(str_detect(Partition,'hawkmem')) %>% summary %>% partfilter('hawkmem',hawkmem) -> hawkmemtotal
jobsthisay %>% filter(str_detect(Partition,'infolab')) %>% summary %>% partfilter('infolab',infolab) -> infolabtotal
rbind(Total_SU_Jobs,ltstotal,im1080total,engtotal,engctotal,himemtotal,engetotal,engitotal,im2080total,chemtotal,healthtotal,
      hawkcputotal,hawkgputotal,hawkmemtotal,infolabtotal) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r annualsummary-serial}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% 
  serial_filter %>% summary %>% parttotalfilter('lts',ltstotal) -> lts_serial
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% 
  serial_filter %>% summary %>% parttotalfilter('im1080',im1080total) -> im1080_serial
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% 
  serial_filter %>% summary %>% parttotalfilter('im2080',im2080total) -> im2080_serial
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% 
  serial_filter %>% summary %>% parttotalfilter('eng',engtotal) -> eng_serial
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% 
  serial_filter %>% summary %>% parttotalfilter('engc',engctotal) -> engc_serial
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% 
  serial_filter %>% summary %>% parttotalfilter('himem',himemtotal) -> himem_serial
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% 
  serial_filter %>% summary %>% parttotalfilter('enge',engetotal) -> enge_serial
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% 
  serial_filter %>% summary %>% parttotalfilter('engi',engitotal) -> engi_serial
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% 
  serial_filter %>% summary %>% parttotalfilter('chem',chemtotal) -> chem_serial
jobsthisay %>% filter(str_detect(Partition,'health')) %>% 
  serial_filter %>% summary %>% parttotalfilter('health',healthtotal) -> health_serial
jobsthisay %>% filter(str_detect(Partition,'hawkcpu') | str_detect(Partition,'hawktest')) %>% 
  serial_filter %>% summary %>% parttotalfilter('hawkcpu',hawkcputotal) -> hawkcpu_serial
jobsthisay %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>% 
  serial_filter %>% summary %>% parttotalfilter('hawkgpu',hawkgputotal) -> hawkgpu_serial
jobsthisay %>% filter(str_detect(Partition,'hawkmem')) %>% 
  serial_filter %>% summary %>% parttotalfilter('hawkmem',hawkmemtotal) -> hawkmem_serial
jobsthisay %>% filter(str_detect(Partition,'infolab')) %>% 
  serial_filter %>% summary %>% parttotalfilter('infolab',infolabtotal) -> infolab_serial
rbind(serialtotal,lts_serial,im1080_serial,eng_serial,engc_serial,himem_serial,enge_serial,engi_serial,im2080_serial,chem_serial,health_serial,
   hawkcpu_serial,hawkgpu_serial,hawkmem_serial,infolab_serial) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r annualsummary-smp}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% 
  smp_filter %>% summary %>% parttotalfilter('lts',ltstotal) -> lts_smp
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% 
  smp_filter %>% summary %>% parttotalfilter('im1080',im1080total) -> im1080_smp
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% 
  smp_filter %>% summary %>% parttotalfilter('im2080',im2080total) -> im2080_smp
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% 
  smp_filter %>% summary %>% parttotalfilter('eng',engtotal) -> eng_smp
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% 
  smp_filter %>% summary %>% parttotalfilter('engc',engctotal) -> engc_smp
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% 
  smp_filter %>% summary %>% parttotalfilter('himem',himemtotal) -> himem_smp
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% 
  smp_filter %>% summary %>% parttotalfilter('enge',engetotal) -> enge_smp
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% 
  smp_filter %>% summary %>% parttotalfilter('engi',engitotal) -> engi_smp
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% 
  smp_filter %>% summary %>% parttotalfilter('chem',chemtotal) -> chem_smp
jobsthisay %>% filter(str_detect(Partition,'health')) %>% 
  smp_filter %>% summary %>% parttotalfilter('health',healthtotal) -> health_smp
jobsthisay %>% filter(str_detect(Partition,'hawkcpu') | str_detect(Partition,'hawktest')) %>% 
  smp_filter %>% summary %>% parttotalfilter('hawkcpu',hawkcputotal) -> hawkcpu_smp
jobsthisay %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>% 
  smp_filter %>% summary %>% parttotalfilter('hawkgpu',hawkgputotal) -> hawkgpu_smp
jobsthisay %>% filter(str_detect(Partition,'hawkmem')) %>% 
  smp_filter %>% summary %>% parttotalfilter('hawkmem',hawkmemtotal) -> hawkmem_smp
jobsthisay %>% filter(str_detect(Partition,'infolab')) %>% 
  smp_filter %>% summary %>% parttotalfilter('infolab',infolabtotal) -> infolab_smp
rbind(smptotal,lts_smp,im1080_smp,eng_smp,engc_smp,himem_smp,enge_smp,engi_smp,im2080_smp,chem_smp,health_smp,
   hawkcpu_smp,hawkgpu_smp,hawkmem_smp,infolab_smp) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r annualsummary-dmp}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('lts',ltstotal) -> lts_dmp
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('im1080',im1080total) -> im1080_dmp
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('im2080',im2080total) -> im2080_dmp
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% 
  dmp_filter %>% summary %>% parttotalfilter('eng',engtotal) -> eng_dmp
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('engc',engctotal) -> engc_dmp
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('himem',himemtotal) -> himem_dmp
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('enge',engetotal) -> enge_dmp
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('engi',engitotal) -> engi_dmp
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('chem',chemtotal) -> chem_dmp
jobsthisay %>% filter(str_detect(Partition,'health')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('health',healthtotal) -> health_dmp
jobsthisay %>% filter(str_detect(Partition,'hawkcpu') | str_detect(Partition,'hawktest')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('hawkcpu',hawkcputotal) -> hawkcpu_dmp
jobsthisay %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('hawkgpu',hawkgputotal) -> hawkgpu_dmp
jobsthisay %>% filter(str_detect(Partition,'hawkmem')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('hawkmem',hawkmemtotal) -> hawkmem_dmp
jobsthisay %>% filter(str_detect(Partition,'infolab')) %>% 
  dmp_filter %>% summary %>% parttotalfilter('infolab',infolabtotal) -> infolab_dmp
rbind(dmptotal,lts_dmp,im1080_dmp,eng_dmp,engc_dmp,himem_dmp,enge_dmp,engi_dmp,im2080_dmp,chem_dmp,health_dmp,
   hawkcpu_dmp,hawkgpu_dmp,hawkmem_dmp,infolab_dmp) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```


Row
--------------------------------------------------

### CPU vs GPU

```{r annualcpuvgpu-summary,echo=F}
jobsthisay %>% summary -> Timing_Total
jobsthisay %>% filter(!str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="cpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> cpu
jobsthisay %>% filter(str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="gpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> gpu
jobsthisay %>% summary %>% 
   mutate(Type="Total","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> total
full_join(full_join(cpu,gpu),total) %>% my_table
```

### Serial Jobs

```{r annualcpuvgpu-serial,echo=F}
jobsthisay %>% serial_filter %>% filter(!str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="cpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> cpu
jobsthisay %>% serial_filter %>% filter(str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="gpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> gpu
jobsthisay %>% serial_filter %>% summary %>% 
   mutate(Type="Total","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> total
full_join(full_join(cpu,gpu),total) %>% my_table
```

### SMP Jobs

```{r annualcpuvgpu-smp,echo=F}
jobsthisay %>% smp_filter %>% filter(!str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="cpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> cpu
jobsthisay %>% smp_filter %>% filter(str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="gpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> gpu
jobsthisay %>% smp_filter %>% summary %>% 
   mutate(Type="Total","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> total
full_join(full_join(cpu,gpu),total) %>% my_table
```

### DMP Jobs

```{r annualcpuvgpu-dmp,echo=F}
jobsthisay %>% dmp_filter %>% filter(!str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="cpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> cpu
jobsthisay %>% dmp_filter %>% filter(str_detect(Partition,"gpu")) %>% summary %>% 
   mutate(Type="gpu","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> gpu
jobsthisay %>% dmp_filter %>% summary %>% 
   mutate(Type="Total","% SU"=round(SU/Timing_Total$SU*100,2),"% Jobs"=round(Jobs/Timing_Total$Jobs*100,2)) %>% 
   select(c("Type","SU","% SU","Jobs","% Jobs","Wait","Run")) -> total
full_join(full_join(cpu,gpu),total) %>% my_table
```

Partition {data-navmenu="Annual Report"}
==============================


Row
---------------------------------

### Summary

```{r annualpart-summary,echo=F}
jobsthisay %>% group_by(Partition) %>% summary -> Timing_Part
jobsthisay %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) %>% mutate('% SU' = round(SU/Timing_Total$SU*100,2)) %>% select(c('Partition','SU','% SU','Jobs', 'Wait', 'Run')) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```


### Serial Jobs

```{r annualpart-serial,echo=F}
jobsthisay %>% serial_filter %>% group_by(Partition) %>% summary  -> Timing_Part
jobsthisay %>% serial_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### SMP Jobs

```{r annualpart-smp,echo=F}
jobsthisay %>% smp_filter %>% group_by(Partition) %>% summary  -> Timing_Part
jobsthisay %>% smp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### DMP Jobs

```{r annualpart-dmp,echo=F}
jobsthisay %>% dmp_filter %>% group_by(Partition) %>% summary  -> Timing_Part
jobsthisay %>% dmp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```





Allocation {data-navmenu="Annual Report"}
==============================

Row
---------------------------------

### Summary

```{r annualalloc-summary,echo=F}
jobsthisay %>% group_by(Account) %>% summary  -> Timing_Part
jobsthisay %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### CPU vs GPU

```{r annualalloc-type,echo=F}
jobsthisay %>% cpu_gpu_total(Account) -> total
jobsthisay %>% cpu_total(Account) -> cpu
jobsthisay %>% gpu_total(Account) -> gpu
full_join(total,full_join(cpu,gpu)) -> usage1920
usage1920[is.na(usage1920)] <- 0
usage1920 %>% mutate('%CPU'=round(CPU/Total*100,2), '%GPU'=round(GPU/Total*100,2)) %>% my_table
```


### Serial Jobs

```{r annualalloc-serial,echo=F}
jobsthisay %>% serial_filter %>% group_by(Account) %>% summary  -> Timing_Part
jobsthisay %>% serial_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table 
```

### SMP Jobs

```{r annualalloc-smp,echo=F}
jobsthisay %>% smp_filter %>% group_by(Account) %>% summary  -> Timing_Part
jobsthisay %>% smp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### DMP Jobs

```{r annualalloc-dmp,echo=F}
jobsthisay %>% dmp_filter %>% group_by(Account) %>% summary  -> Timing_Part
jobsthisay %>% dmp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table 
```

User {data-navmenu="Annual Report"}
==============================

Row
---------------------------------

### Summary

```{r annualuser-summary}
jobsthisay %>% group_by(User) %>% summary  -> Timing_Part
jobsthisay %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### CPU vs GPU

```{r annualuser-type,echo=F}
jobsthisay %>% cpu_gpu_total(User) -> total
jobsthisay %>% cpu_total(User) -> cpu
jobsthisay %>% gpu_total(User) -> gpu
full_join(total,full_join(cpu,gpu)) -> usage1920
usage1920[is.na(usage1920)] <- 0
usage1920 %>% mutate('%CPU'=round(CPU/Total*100,2), '%GPU'=round(GPU/Total*100,2)) %>% my_table
```

### Serial

```{r annualuser-serial}
jobsthisay %>% serial_filter %>% group_by(User) %>% summary  -> Timing_Part
jobsthisay %>% serial_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table 
```

### SMP

```{r annualuser-smp}
jobsthisay %>% smp_filter %>% group_by(User) %>% summary  -> Timing_Part
jobsthisay %>% smp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```

### DMP

```{r annualuser-dmp}
jobsthisay %>% dmp_filter %>% group_by(User) %>% summary  -> Timing_Part
jobsthisay %>% dmp_filter %>% summary -> Timing_Total

full_join(Timing_Part,Timing_Total) -> Timing
Timing[is.na(Timing)] <- "Total"

Timing %>% my_table
```


Summary {data-navmenu="Monthly Reports"}
=========================================

Row 
------------------------------------

### Summary

```{r monthly-setup,echo=F}
jobsthisay %>% monthly_summary %>% partpercent(ay2021su[1:currmonth]) -> total
jobsthisay %>% serial_filter %>% monthly_summary -> serial
jobsthisay %>% smp_filter %>% monthly_summary -> smp
jobsthisay %>% dmp_filter %>% monthly_summary -> dmp

getpercent(serial,percent) -> serialpercent
getpercent(smp,percent) -> smppercent
getpercent(dmp,percent) -> dmppercent

#cbind(total,serialpercent,smppercent,dmppercent)  %>% select(-c(Year1,Month1,Year2,Month2,Year3,Month3)) -> jobtotal
#colnames(jobtotal) <- c("Year","Month","SU","Jobs","Wait","Run","SU","Jobs","% SU","%Jobs","Wait","Run","SU","Jobs","% SU","%Jobs","Wait","Run","SU","Jobs","% SU","%Jobs","Wait","Run")
#jobtotal %>% 
#  kable() %>%
#  kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive")) %>%
#  add_header_above(c(" " = 2, "Total" = 4, "Serial" = 6, "SMP" = 6, "DMP" = 6))
```


```{r monthly-summary}
total %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### CPU vs GPU

```{r monthly-summarytype, echo=F}
jobsthisay %>% cpu_gpu_monthly -> total
jobsthisay %>% cpu_monthly -> cpu
jobsthisay %>% gpu_monthly -> gpu
full_join(total,full_join(cpu,gpu)) %>% mutate('%CPU'=round(CPU/Total*100,2), '%GPU'=round(GPU/Total*100,2)) -> usage1920
usage1920 %>% kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthly-serial}
serialpercent %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthly-smp}
smppercent %>% 
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthly-dmp}
dmppercent %>% 
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Partition {data-navmenu="Monthly Reports"}
===============================================

Row 
------------------------------------------

### lts

```{r monthlypart-lts}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% monthly_summary %>% partpercent(lts[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-lts-serial}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% serial_filter %>% monthly_summary %>% 
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthly-part-lts-smp}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-lts-dmp}
jobsthisay %>% filter(str_detect(Partition,'lts')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### im1080

```{r monthlypart-im1080}
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% monthly_summary %>% partpercent(im1080[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-im1080-serial}
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-im1080-smp}
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-im1080-dmp}
jobsthisay %>% filter(str_detect(Partition,'im1080')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### eng

```{r monthlypart-eng}
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% monthly_summary %>% partpercent(eng[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-eng-serial}
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-eng-smp}
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-eng-dmp}
jobsthisay %>% filter(Partition=="eng" | Partition=="eng-gpu") %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### engc

```{r monthlypart-engc}
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% monthly_summary %>% partpercent(engc[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-engc-serial}
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-engc-smp}
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-engc-dmp}
jobsthisay %>% filter(str_detect(Partition,'engc')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### himem

```{r monthlypart-himem}
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% monthly_summary %>% partpercent(himem[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-himem-serial}
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-himem-smp}
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-himem-dmp}
jobsthisay %>% filter(str_detect(Partition,'himem')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### enge

```{r monthlypart-enge}
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% monthly_summary %>% partpercent(enge[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-enge-serial}
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-enge-smp}
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-enge-dmp}
jobsthisay %>% filter(str_detect(Partition,'enge')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### engi

```{r monthlypart-engi}
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% monthly_summary %>% partpercent(engi[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-engi-serial}
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-engi-smp}
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-engi-dmp}
jobsthisay %>% filter(str_detect(Partition,'engi')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```



Row 
------------------------------------------

### im2080

```{r monthlypart-im2080}
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% monthly_summary %>% partpercent(im2080[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-im2080-serial}
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-im2080-smp}
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-im2080-dmp}
jobsthisay %>% filter(str_detect(Partition,'im2080')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### chem

```{r monthlypart-chem}
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% monthly_summary %>% partpercent(chem[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-chem-serial}
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-chem-smp}
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-chem-dmp}
jobsthisay %>% filter(str_detect(Partition,'chem')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### health

```{r monthlypart-health}
jobsthisay %>% filter(str_detect(Partition,'health')) %>% monthly_summary %>% partpercent(health[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-health-serial}
jobsthisay %>% filter(str_detect(Partition,'health')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-health-smp}
jobsthisay %>% filter(str_detect(Partition,'health')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-health-dmp}
jobsthisay %>% filter(str_detect(Partition,'health')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### hawkcpu

```{r monthlypart-hawkcpu}
jobsthisay %>% filter(str_detect(Partition,'hawkcpu') | str_detect(Partition,'hawktest')) %>% monthly_summary %>% partpercent(hawkcpu[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-hawkcpu-serial}
jobsthisay %>% filter(str_detect(Partition,'hawkcpu') | str_detect(Partition,'hawktest')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-hawkcpu-smp}
jobsthisay %>% filter(str_detect(Partition,'hawkcpu') | str_detect(Partition,'hawktest')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-hawkcpu-dmp}
jobsthisay %>% filter(str_detect(Partition,'hawkcpu') | str_detect(Partition,'hawktest')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### hawkgpu

```{r monthlypart-hawkgpu}
jobsthisay %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>% monthly_summary %>% partpercent(hawkgpu[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-hawkgpu-serial}
jobsthisay %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-hawkgpu-smp}
jobsthisay %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-hawkgpu-dmp}
jobsthisay %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```


Row 
------------------------------------------

### hawkmem

```{r monthlypart-hawkmem}
jobsthisay %>% filter(str_detect(Partition,'hawkmem')) %>% monthly_summary %>% partpercent(hawkmem[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-hawkmem-serial}
jobsthisay %>% filter(str_detect(Partition,'hawkmem')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-hawkmem-smp}
jobsthisay %>% filter(str_detect(Partition,'hawkmem')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-hawkmem-dmp}
jobsthisay %>% filter(str_detect(Partition,'hawkmem')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

Row 
------------------------------------------

### infolab

```{r monthlypart-infolab}
jobsthisay %>% filter(str_detect(Partition,'infolab')) %>% monthly_summary %>% partpercent(infolab[1:currmonth]) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### Serial Jobs

```{r monthlypart-infolab-serial}
jobsthisay %>% filter(str_detect(Partition,'infolab')) %>% serial_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### SMP Jobs

```{r monthlypart-infolab-smp}
jobsthisay %>% filter(str_detect(Partition,'infolab')) %>% smp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```

### DMP Jobs

```{r monthlypart-infolab-dmp}
jobsthisay %>% filter(str_detect(Partition,'infolab')) %>% dmp_filter %>% monthly_summary %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive") )
```













Allocation {data-navmenu="Monthly Reports"}
==========================================

Row
---------------------------------

### List of PIs

```{r monthlyalloc-list,echo=F}
jobsthisay$Account %>% unique %>% sort %>% matrix(ncol = 1) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped", full_width = F)
```

### Summary

```{r monthlyalloc-summary,echo=F}
jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>%
  group_by(Year,Month,Account) %>%
  summary %>%
  my_longtable
```

### Partition

```{r monthlyalloc-part,echo=F}
jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>%
  group_by(Year,Month,Account,Partition) %>%
  summary %>%
  my_longtable
```

User {data-navmenu="Monthly Reports"}
==========================================

Row
---------------------------------

### List of Users

```{r monthlyuser-list,echo=F}
jobsthisay$User %>% unique %>% sort %>% matrix(ncol = 1) %>% 
  kable() %>% kable_styling(bootstrap_options = "striped")
```

### Summary

```{r monthlyuser-summary,echo=F}
jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>%
  group_by(Year,Month,User,Account) %>%
  summary %>%
  my_longtable
```

### Partition

```{r monthlyuser-part,echo=F}
jobsthisay %>% 
  mutate(Year=year(End),Month=month(End,label=TRUE)) %>%
  group_by(Year,Month,User,Account,Partition) %>%
  summary %>%
  my_longtable
```

Energy Consumption {data-navmenu="Monthly Reports"} 
=====================================================

Row
-------------------------------------------

### Total 

```{r monthlyenergy-total}
monthlypower2021 %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### lts

```{r monthlyenergy-lts}
monthlypower2021 %>% filter(str_detect(Partition,'lts')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage(kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```


### im1080

```{r monthlyenergy-im1080}
monthlypower2021 %>% filter(str_detect(Partition,'im1080')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```


### eng

```{r monthyenergy-eng}
monthlypower2021 %>% filter(Partition=="eng" | Partition=="eng-gpu") %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### engc

```{r monthlyenergy-engc}
monthlypower2021 %>% filter(str_detect(Partition,'engc')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

Row
---------------------------------------------


```{r monthlyenergy-himem}
### himem
# himem node can only measure volts, no amp or watts skipping this node
#monthlypower2021 %>% filter(str_detect(Partition,'himem')) %>%
#  group_by(Year,Month) %>%
#  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
#  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### enge

```{r monthlyenergy-enge}
monthlypower2021 %>% filter(str_detect(Partition,'enge')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### engi

```{r monthlyenergy-engi}
monthlypower2021 %>% filter(str_detect(Partition,'engi')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### im2080

```{r monthlyenergy-im2080}
monthlypower2021 %>% filter(str_detect(Partition,'im2080')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### chem

```{r monthlyenergy-chem}
monthlypower2021 %>% filter(str_detect(Partition,'chem')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### health

```{r monthlyenergy-health}
monthlypower2021 %>% filter(str_detect(Partition,'health')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

Row
---------------------------------------------

### hawkcpu

```{r monthlyenergy-hawkcpu}
monthlypower2021 %>% filter(str_detect(Partition,'hawkcpu')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### hawkgpu

```{r monthlyenergy-hawkgpu}
monthlypower2021 %>% filter(str_detect(Partition,'hawkgpu') | str_detect(Partition,'hawktest')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### hawkmem

```{r monthlyenergy-hawkmem}
monthlypower2021 %>% filter(str_detect(Partition,'hawkmem')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```

### infolab

```{r monthlyenergy-infolab}
monthlypower2021 %>% filter(str_detect(Partition,'infolab')) %>%
  group_by(Year,Month) %>%
  summarize('Average Power Usage (kW)'=round(sum(Power)/1000,2),'Energy Consumption (MWh)'=round(sum(Energy)/1000,2)) %>%
  kable() %>% kable_styling(bootstrap_options = c("striped", "hover", "bordered", "condensed", "responsive"))
```


Row
---------------------------------------------

### Energy Consumption per Server

```{r monthylenergy-server}
monthlypower2021 %>%
  group_by(Year,Month,Partition,Host) %>%
  summarize('Average Power Usage (W)'=round(sum(Power),2),'Energy Consumption (kWh)'=round(sum(Energy),2)) %>%
  my_longtable  
```



Jobs Completed 
==========================================

Row {.tabset data-height=1500}
----------------------------------

### January

```{r january,echo=F}
monthly_usage( jobsthisay, as.Date("2021-01-01"), as.Date("2021-02-01") )
```

### February

```{r february,echo=F}
monthly_usage( jobsthisay, as.Date("2021-02-01"), as.Date("2021-03-01") )
```

### March

```{r march,echo=F}
monthly_usage( jobsthisay, as.Date("2021-03-01"), as.Date("2021-04-01") )
```

### April

```{r april,echo=F}
monthly_usage( jobsthisay, as.Date("2021-04-01"), as.Date("2021-05-01") )
```

### May

```{r may,echo=F}
monthly_usage( jobsthisay, as.Date("2021-05-01"), as.Date("2021-06-01") )
```

### June

```{r june,echo=F}
monthly_usage( jobsthisay, as.Date("2021-06-01"), as.Date("2021-07-01") )
```

### July

```{r july,echo=F}
monthly_usage( jobsthisay, as.Date("2021-07-01"), as.Date("2021-08-01") )
```

### August

```{r august,echo=F}
monthly_usage( jobsthisay, as.Date("2021-08-01"), as.Date("2021-09-01") )
```

### September

```{r september,echo=F}
monthly_usage( jobsthisay, as.Date("2021-09-01"), as.Date("2021-10-01") )
```

### October

```{r october,echo=F}
monthly_usage( jobsthisay, as.Date("2021-10-01"), as.Date("2021-11-01") )
```

### November

```{r november,echo=F}
monthly_usage( jobsthisay, as.Date("2021-11-01"), as.Date("2021-12-01") )
```

### December

```{r december,echo=F}
monthly_usage( jobsthisay, as.Date("2021-12-01"), as.Date("2022-01-01") )
```

