AY 2018-19 {data-navmenu="Annual Reports"}
=====================================================================

Row
-----------------------------------------------------------------------

```{r ay1819_monthly_setup}
daily_summary <- daily %>%  filter(Day >= as.Date("2018-10-01") & Day < as.Date("2019-10-01")) %>%
  group_by(Day) %>%
  summarize(Total=sum(as.double(Total)),
            Jobs=sum(as.double(TotalJ)),
            Serial=sum(as.double(Serial)),
            SerialJ=sum(as.double(SerialJ)),
            Single=sum(as.double(Single)),
            SingleJ=sum(as.double(SingleJ)),
            Multi=sum(as.double(Multi)),
            MultiJ=sum(as.double(MultiJ))) %>%
  drop_na()

dailypwrconsump <- dailypower %>%  filter(Date >= as.Date("2018-10-01") & Date < as.Date("2019-10-01"))

data_tmp <- data %>% select(V1,V2) %>%
	filter(as.Date(V1) >= as.Date("2018-10-01") & as.Date(V1) < as.Date("2019-10-01"))
datagpu_tmp <-  datagpu %>% mutate(V12=V2+V4+V6+V8+V10) %>% select(V1,V12) %>%
	filter(as.Date(V1) >= as.Date("2018-10-01") & as.Date(V1) < as.Date("2019-10-01"))
data_cpu_gpu <- full_join(data_tmp,datagpu_tmp) %>% mutate(V3=V2-V12)
dayslice <- length(data_cpu_gpu$V1)
d1 <- seq(as.POSIXct(data_cpu_gpu[1,1]), by = "days", length = dayslice)
dateWindow = c(as.Date("2018-10-01"), as.Date("2019-09-30") )

monthlyreport <- monthly %>% ay1819filter %>% 
  group_by(Month) %>%	
  summarize(Total=round(sum(as.double(Total)),2),User=n_distinct(Name),Jobs=round(sum(as.double(TotalJ))))

pireport <- monthly %>% ay1819filter %>% 
  group_by(PI) %>% 
  summarize(Total=round(sum(as.double(Total)),2),User=n_distinct(Name),Jobs=round(sum(as.double(TotalJ)))) 

pideptreport <- monthly %>% ay1819filter %>% 
  group_by(PIDept) %>% 
  summarize(Total=round(sum(as.double(Total)),2),User=n_distinct(Name),Jobs=round(sum(as.double(TotalJ))))

deptreport <- monthly %>% ay1819filter %>% 
  group_by(Department) %>% 
  summarize(Total=round(sum(as.double(Total)),2),User=n_distinct(Name),Jobs=round(sum(as.double(TotalJ))))

userusage <- monthly %>% ay1819filter %>% 
  group_by(Status) %>% 
  summarize(Total=round(sum(as.double(Total)),2),User=n_distinct(Name),Jobs=round(sum(as.double(TotalJ))))

users <- monthly %>% ay1819filter %>%
  group_by(Name) %>%
  summarize(Total=sum(as.double(Total)))

pis <- monthly %>% ay1819filter %>%
  group_by(PI) %>%
  summarize(Total=sum(as.double(Total)),Jobs=sum(as.double(TotalJ)))

pidept <- monthly %>% ay1819filter %>%
  group_by(PIDept) %>%
  summarize(Total=sum(as.double(Total)))

dept <- monthly %>% ay1819filter %>%
  group_by(Department) %>%
  summarize(Total=sum(as.double(Total)))

months_sofar <- length(monthlyreport$Month)

forttotal <- sum(pis$Total)
fortusage <- round(forttotal/(sum(ay1819su[1:months_sofar]))*100)
fortjobs <- sum(pis$Jobs)
```

### Active Users

```{r ay1819_users}
valueBox(n_distinct(users$Name), icon = "fa-users")
```

### Active PIs

```{r ay1819_pis}
valueBox(n_distinct(pis$PI), icon = "fa-user-md")
```

### PI Departments

```{r ay1819_pidept}
valueBox(n_distinct(pidept$PIDept), icon = "fa-building")
```

### Users Major/Department

```{r ay1819_userdept}
valueBox(n_distinct(dept$Department), icon = "fa-university")
```


### Jobs Run

```{r ay1819_jobs}
valueBox(fortjobs, icon = "fa-desktop")
```

### % of SUs consumed

```{r ay1819_sus}
gauge(fortusage, min = 0, max = 100, symbol = '%', gaugeSectors(
success = c(71, 100), warning = c(50, 70), danger = c(0, 49)
))
```

Row {.tabset}
--------------------------------

### Top 10 Users by SUs consumed

```{r ay1819_users_sus}
monthly %>% ay1819filter %>% topuserstotal 
```


### Top 10 Users by Jobs 

```{r ay1819_users_jobs}
monthly %>% ay1819filter %>% topusersjobs
```

### Top PIs

```{r ay1819_pis_sus-jobs}
monthly %>% ay1819filter %>%
	group_by(PI,Department=PIDept) %>%
	summarize(SUs=sum(round(as.double(Total))),Jobs=sum(round(as.double(TotalJ)))) %>%
	arrange(desc(SUs),desc(Jobs)) %>% head(25) %>% 
	datatable(rownames=FALSE,options=list(dom = 't', autoWidth = TRUE))
```	

### Top Majors 

```{r ay1819_majors_sus-jobs}
monthly %>% ay1819filter %>%
	group_by(Major=Department,Status) %>%
	summarize(Users=n_distinct(Name),SUs=sum(round(as.double(Total))),Jobs=sum(round(as.double(TotalJ)))) %>%
	arrange(desc(SUs),desc(Jobs),desc(Users)) %>% head(25) %>%
	datatable(rownames=FALSE,options=list(dom='t', autoWidth = TRUE))
```

### Top Departments

```{r ay1819_pidept_sus-jobs}
monthly %>% ay1819filter %>%
	group_by(Department=PIDept) %>%
	summarize(PI=n_distinct(PI),Users=n_distinct(Name),SUs=sum(round(as.double(Total))),Jobs=sum(round(as.double(TotalJ)))) %>%
	arrange(desc(SUs),desc(Jobs),desc(PI),desc(Users)) %>% head(25) %>% 
	datatable(rownames=FALSE,options=list(dom = 't', autoWidth = TRUE))
```	

### Usage

```{r ay1819_usage_all}
dygraph( xts(cbind(data_cpu_gpu$V2,data_cpu_gpu$V3,data_cpu_gpu$V12), order.by = d1)) %>%
	dySeries("V1", label = "Total", color = "black") %>%
	dySeries("V2", label = "CPU", color = "blue") %>%
	dySeries("V3", label = "GPU", color = "green") %>%
	dyAxis("y", label = "SUs consumed") %>%
	dyRoller(rollPeriod = 7) %>%
	dyHighlight(highlightSeriesOpts = list(strokeWidth = 2)) %>%
	dyRangeSelector( dateWindow = dateWindow ) 
```

### Jobs

```{r ay1819_jobs_all}
dygraph( xts(daily_summary$Jobs, order.by = daily_summary$Day)) %>%
        dySeries("V1", label = "Total", color = "black") %>%
        dyAxis("y", label = "Number of Jobs") %>%
        dyRoller(rollPeriod = 7) %>%
        dyHighlight(highlightSeriesOpts = list(strokeWidth = 2)) %>%
        dyRangeSelector( dateWindow = dateWindow )
```

### Usage by Type

```{r ay1819_su_jobtype_all}
dygraph( xts(cbind(daily_summary$Serial,daily_summary$Single,daily_summary$Multi), order.by = daily_summary$Day)) %>%
        dySeries("V1", label = "Serial", color = "black") %>%
        dySeries("V2", label = "Single", color = "blue") %>%
        dySeries("V3", label = "Multi", color = "green") %>%
        dyAxis("y", label = "SUs Consumed") %>%
        dyRoller(rollPeriod = 7) %>%
        dyHighlight(highlightSeriesOpts = list(strokeWidth = 2)) %>%
        dyRangeSelector( dateWindow = dateWindow )
```

### Jobs by Type

```{r ay1819_jobs_jobtype_all}
dygraph( xts(cbind(daily_summary$SerialJ,daily_summary$SingleJ,daily_summary$MultiJ), order.by = daily_summary$Day)) %>%
        dySeries("V1", label = "Serial", color = "black") %>%
        dySeries("V2", label = "Single", color = "blue") %>%
        dySeries("V3", label = "Multi", color = "green") %>%
        dyAxis("y", label = "SUs Consumed") %>%
        dyRoller(rollPeriod = 7) %>%
        dyHighlight(highlightSeriesOpts = list(strokeWidth = 2)) %>%
        dyRangeSelector( dateWindow = dateWindow )
```

### Power Consumption

```{r ay1819_powerconsump}
dygraph( xts(dailypwrconsump$Energy, order.by = dailypwrconsump$Date)) %>%
        dySeries("V1", label = "Energy", color = "black") %>%
        dyAxis("y", label = "Average Daily Energy consumption (Wh)") %>%
        dyOptions(labelsKMB = TRUE) %>%
        dyRoller(rollPeriod = 7) %>%
        dyHighlight(highlightSeriesOpts = list(strokeWidth = 2)) %>%
        dyRangeSelector( dateWindow = dateWindow )
```

Row {.tabset}
----------------------------------------------------------------------

### Monthly Usage


```{r ay1819_monthly_usage}
monthlyreport %>% 
  mutate(Available=ay1819su[1:months_sofar],Unused=Available-Total,Percent=round(Total/Available*100,2)) %>%
  plot_ly(x = ~Month, y = ~Total, type = "bar", name = "Consumed" ) %>%
    add_trace(y =  ~ Unused, name = "Unused") %>%
    layout(yaxis = list(title = 'SUs Consumed' ), xaxis = list(title = 'Month' ), barmode = 'stack')
```

### Usage Percentage

```{r ay1819_monthly_usage_percent}
usage <- round(sum(monthlyreport$Total)/sum(ay1819su)*100,2)
monthlyreport %>% 
  mutate(Available=ay1819su,
     Unused=round((Available-Total)/Available*100,2),
     Percent=round(Total/Available*100,2)) %>%
  plot_ly(x = ~Month, y = ~Percent, type = "bar", name = "Consumed" ) %>%
    add_trace(y =  ~ Unused, name = "Unused") %>%
    layout(yaxis = list(title = 'SUs Consumed' ), xaxis = list(title = 'Month' ), barmode = 'stack',
      shapes=list(list(type='line', 
      x0=as.Date("2018-10-01"), x1=as.Date("2019-09-01"), 
      y0= usage, y1= usage, line=list(width=2, color = "green")),
      list(type='line', 
      x0=as.Date("2018-10-01"), x1=as.Date("2019-09-01"), 
      y0= 80, y1= 80, line=list(width=2, color = "red"))
    )
    )
```

### Monthly Energy Consumption

```{r ay1819_monthly_power}
averagepower <- monthlypower %>% ay1819filter %>%
  group_by(Month) %>%
  summarize(Power=round(sum(Power)/1000,2),Energy=round(sum(Energy)/1000,2))
monthlypower %>% ay1819filter %>%
  group_by(Month) %>%
  summarize(Power=round(sum(Power)/1000,2),Energy=round(sum(Energy)/1000,2)) %>%
  plot_ly(x = ~Month, y = ~Energy, type = "bar", name = "Energy Consumption" ) %>%
    layout(yaxis = list(title = 'Energy Consumed (MWh)' ), xaxis = list(title = 'Month' ),
      shapes=list(list(type='line',
      x0=as.Date("2018-10-01"), x1=as.Date("2019-09-01"),
      y0= mean(averagepower$Energy), y1= mean(averagepower$Energy), line=list(width=2, color = "green")))
    )
```

Row 
----------------------------------------------------------------------

### SUs Consumed by PI

```{r ay1819_pis_sus}
plot_ly(pireport, x = ~Total, y = ~reorder(PI, Total), type = "bar", name = "PI Usage Report", orientation = 'h') %>%
  layout(xaxis = list(title = '', type = 'log' ), 
     yaxis = list(title = '' ),
     margin = list(l = 200, r = 20, t = 25, b = 25))
```

### Active Users By PI

```{r ay1819_pis_users}
plot_ly(pireport, values = ~User, labels = ~PI, type = "pie", textposition = 'inside', textinfo = 'label', showlegend = F)
```

Row 
----------------------------------------------------------------------

### SUs Consumed by Department

```{r ay1819_pidept_sus}
plot_ly(pideptreport, x = ~Total, y = ~reorder(PIDept, Total), type = "bar", name = "PI Usage Report", orientation = 'h') %>%
  layout(xaxis = list(title = '', type = 'log' ), 
     yaxis = list(title = '' ),
     margin = list(l = 200, r = 20, t = 25, b = 25))
```

### Active Users By Department

```{r ay1819_pidept_users}
plot_ly(pideptreport, values = ~User, labels = ~PIDept, type = "pie", textposition = 'inside', textinfo = 'label', showlegend = F)
```

Row 
----------------------------------------------------------------------

### SUs Consumed by Users Department/Major

```{r ay1819_userdept_sus}
plot_ly(deptreport, x = ~Total, y = ~reorder(Department, Total), type = "bar", name = "PI Usage Report", orientation = 'h') %>%
  layout(xaxis = list(title = '', type = 'log' ), 
   yaxis = list(title = '' ),
   margin = list(l = 200, r = 20, t = 25, b = 25))
```

### Active Users By Department/Major

```{r ay1819_userdept_users}
plot_ly(deptreport, values = ~User, labels = ~Department, type = "pie", textposition = 'inside', textinfo = 'label', showlegend = F) 
```

Row
----------------------------------------------------------------------

### SUs Consumed by Status

```{r ay1819_users_status_sus}
plot_ly(userusage, x = ~Total, y = ~Status, type = "bar", name = "PI Usage Report", orientation = 'h') %>%
  layout(xaxis = list(title = ' ', type = 'log' ), 
   yaxis = list(title = '' ),
   margin = list(l = 200, r = 20, t = 25, b = 25))
```

### Active Users By Status

```{r ay1819_users_status_num}
plot_ly(userusage, values = ~User, labels = ~Status, type = "pie", textposition = 'inside', textinfo = 'label', showlegend = F) 
```

AY 2018-19 {data-navmenu="Job Types"}
===========================================================


Row
-----------------------------------------------------------

### Description

There are three types of jobs that can be run on Sol

*  __Single__: These are jobs that request only one compute core including GPU jobs.
*  __SMP__: These are jobs that request only one node and more than one core. These could be symmetric multi threaded jobs and a bunch of __Single__ jobs run in parallel. These jobs do not utilize more than one node and do not use the infiniband fabric.
* __Multi__: These are jobs that request more than one node. These are jobs are primarily distributed parallel or mpi jobs that make use of the infiniband fabric. These jobs also include __Single__ or __SMP__ jobs that are distributed across the requested nodes and/or compute cores that do not use the infiniband fabric.

 
Row {.tabset}
-----------------------------------------------------------

### SUs Consumed 

```{r ay1819_sus_jobtype}
monthly %>%
  group_by(Month) %>%
  ay1819filter %>%
  summarize(Serial=sum(as.double(Serial)),
    Single=sum(as.double(Single)),
    Multi=sum(as.double(Multi)),
    Total=sum(as.double(Total))) %>%
  plot_ly(x = ~Month, y = ~Serial, type = "bar", name = "Single" ) %>%
    add_trace(y =  ~Single, name = "SMP") %>%
    add_trace(y =  ~Multi, name = "Multi") %>%
    layout(yaxis = list(title = ' ' ), xaxis = list(title = 'Month' ), barmode = 'stack')
```

 
### Number of Jobs

```{r ay1819_jobs_jobtype}
monthly %>%
  group_by(Month) %>%
  ay1819filter %>%
  summarize(SerialJ=sum(as.double(SerialJ)),
    SingleJ=sum(as.double(SingleJ)),
    MultiJ=sum(as.double(MultiJ)),
    TotalJ=sum(as.double(TotalJ))) %>%
  plot_ly(x = ~Month, y = ~SerialJ, type = "bar", name = "Single" ) %>%
    add_trace(y =  ~SingleJ, name = "SMP") %>%
    add_trace(y =  ~MultiJ, name = "Multi") %>%
    layout(yaxis = list(title = ' ' ), xaxis = list(title = 'Month' ), barmode = 'stack')
```

### SUs Consumed by %

```{r ay1819_sus_percent_jobtype}
monthly %>%
  group_by(Month) %>%
  ay1819filter %>%
  summarize(Serial=sum(as.double(Serial)),
    Single=sum(as.double(Single)),
    Multi=sum(as.double(Multi)),
    Total=sum(as.double(Total))) %>%
  mutate(Serial=round(Serial/Total*100,2),Single=round(Single/Total*100,2),Multi=round(Multi/Total*100,2)) %>%
  plot_ly(x = ~Month, y = ~Serial, type = "bar", name = "Single" ) %>%
    add_trace(y =  ~Single, name = "SMP") %>%
    add_trace(y =  ~Multi, name = "Multi") %>%
    layout(yaxis = list(title = ' ' ), xaxis = list(title = 'Month' ), barmode = 'stack')
```

 
### Number of Jobs by %

```{r ay1819_jobs_percent_jobtype}
monthly %>%
  group_by(Month) %>%
  ay1819filter %>%
  summarize(SerialJ=sum(as.double(SerialJ)),
    SingleJ=sum(as.double(SingleJ)),
    MultiJ=sum(as.double(MultiJ)),
    TotalJ=sum(as.double(TotalJ))) %>%
  mutate(SerialJ=round(SerialJ/TotalJ*100,2),SingleJ=round(SingleJ/TotalJ*100,2),MultiJ=round(MultiJ/TotalJ*100,2)) %>%
  plot_ly(x = ~Month, y = ~SerialJ, type = "bar", name = "Single" ) %>%
    add_trace(y =  ~SingleJ, name = "SMP") %>%
    add_trace(y =  ~MultiJ, name = "Multi") %>%
    layout(yaxis = list(title = ' ' ), xaxis = list(title = 'Month' ), barmode = 'stack')
```

Row {.tabset data-height=1600}
----------------------------------------------------

### SUs Consumed

```{r ay1819_pi_sus_jobtype}
monthly %>%
  group_by(PI) %>%
  ay1819filter %>%
  summarize(Serial=sum(as.double(Serial)),
    Single=sum(as.double(Single)),
    Multi=sum(as.double(Multi)),
    Total=sum(as.double(Total))) %>%
  plot_ly(x = ~Serial, y = ~reorder(PI,Total), type = "bar", name = "Single",  orientation = 'h' ) %>%
    add_trace(x =  ~Single, name = "SMP") %>%
    add_trace(x =  ~Multi, name = "Multi") %>%
    layout(xaxis = list(title = '', type = 'log' ), yaxis = list(title = '' ), barmode = 'stack', margin = list(l = 200, r = 20, t = 25, b = 25) )
``` 

### Number of Jobs

```{r ay1819_pi_jobs_jobtype}
monthly %>%
  group_by(PI) %>%
  ay1819filter %>%
  summarize(SerialJ=sum(as.double(SerialJ)),
    SingleJ=sum(as.double(SingleJ)),
    MultiJ=sum(as.double(MultiJ)),
    TotalJ=sum(as.double(TotalJ)),Total=sum(as.double(Total))) %>%
  plot_ly(x = ~SerialJ, y = ~reorder(PI,Total), type = "bar", name = "Single",  orientation = 'h' ) %>%
    add_trace(x =  ~SingleJ, name = "SMP") %>%
    add_trace(x =  ~MultiJ, name = "Multi") %>%
    layout(xaxis = list(title = '', type = 'log' ), yaxis = list(title = '' ), barmode = 'stack', margin = list(l = 200, r = 20, t = 25, b = 25) )
``` 

### SUs Consumed by %

```{r ay1819_pi_sus_percent_jobtype}
monthly %>%
  group_by(PI) %>%
  ay1819filter %>%
  summarize(Serial=sum(as.double(Serial)),
    Single=sum(as.double(Single)),
    Multi=sum(as.double(Multi)),
    Total=sum(as.double(Total))) %>%
  mutate(Serial=round(Serial/Total*100,2),Single=round(Single/Total*100,2),Multi=round(Multi/Total*100,2)) %>%
  plot_ly(x = ~Serial, y = ~reorder(PI,Total), type = "bar", name = "Single",  orientation = 'h' ) %>%
    add_trace(x =  ~Single, name = "SMP") %>%
    add_trace(x =  ~Multi, name = "Multi") %>%
    layout(xaxis = list(title = '' ), yaxis = list(title = '' ), barmode = 'stack', margin = list(l = 200, r = 20, t = 25, b = 25) )
``` 

### Number of Jobs by %

```{r ay1819_pi_jobs_percent_jobtype}
monthly %>%
  group_by(PI) %>%
  ay1819filter %>%
  summarize(SerialJ=sum(as.double(SerialJ)),
    SingleJ=sum(as.double(SingleJ)),
    MultiJ=sum(as.double(MultiJ)),
    TotalJ=sum(as.double(TotalJ)),
    Total=sum(as.double(Total))) %>%
  mutate(SerialJ=round(SerialJ/TotalJ*100,2),SingleJ=round(SingleJ/TotalJ*100,2),MultiJ=round(MultiJ/TotalJ*100,2)) %>%
  plot_ly(x = ~SerialJ, y = ~reorder(PI,Total), type = "bar", name = "Single",  orientation = 'h' ) %>%
    add_trace(x =  ~SingleJ, name = "SMP") %>%
    add_trace(x =  ~MultiJ, name = "Multi") %>%
    layout(xaxis = list(title = '' ), yaxis = list(title = '' ), barmode = 'stack', margin = list(l = 200, r = 20, t = 25, b = 25) )
```


